---
title: "Income and Ideology"
author: "Your Name Here"
date: "April 13, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(primer.data)
library(tidyverse)
library(rstanarm)
library(tidybayes)

# Check out the raw cces tibble, especially the faminc (family income) and
# ideology variables.

x <- cces %>% 
  filter(year == 2019) %>% 
  select(state, gender, age, race, faminc, ideology) %>% 
  drop_na() %>% 
  
  # This is an absurd hack. Do not do this, ever. This only works because, if
  # you coerce factor variables into integers, the order of the factor levels is
  # preserved. So, low numbers for faminc/ideology correspond to poorer/liberal
  # individuals.
  
  # We need the variables, at least faminc, to be numeric so that we can create
  # a statistical model using the tools we have learned.
  
  mutate(faminc = as.integer(faminc)) %>% 
  mutate(ideology = as.integer(ideology))
```


```{r setup, include=FALSE}
plot_1<- x %>%
  ggplot(aes(x = faminc, y = ideology)) +
  geom_jitter(alpha = 0.5) + 
  geom_smooth(formula = y ~ x,
              method = "lm")



  
```

```{r}
plot_1
```

*Describe the relationship between ideology and family income. How does it vary by gender? Does your conclusion change if we "adjust" for race and age?*


## Wisdom


## Justice
$y_i = \beta_0 + \beta_1x + \varepsilon_i$
$ideology_i=\beta_0 + \beta_1faminc_i + \varepsilon_i$

-higher the family income, the lower the ideology score(more liberal)

## Courage
```{r}
fit_1 <- stan_glm(data = x,
                  formula = ideology ~ faminc,
                  refresh = 0)
fit_1
print(fit_1, digits = 3)
```
beta_0 = intercept, when income is zero, ideology is 3.471(slightly left of center)
3.471 is the median of the pposterior distribution, 95% confidence interval is between +/- .05


beta_1 = slope = for every one unit increase in income(income bin of $10k), we would expect 
ideology to decrease slightly(.047 more liberal)
**CAUSAL claim- if we change a person's family income then their ideology will change. that's manipulation

when comparing two families that are all-else-equal we would expect the richer family to be more liberal than the poorer family by a margin og -0.047

$$ideology_i = \beta_0 + \beta_1 faminc + \beta_2 gender + \beta_3 faminc+gender +
\epsilon_i$$
```{r}
fit_2 <- stan_glm(data = x,
                  formula = ideology ~ famin + gender + faminc*gender,
                  refresh = 0,
                  seed = 220)

print(fit_2, details = FALSE, digits = 3)
```
-intercept = female and when age equals 0 


```{r}
fit_3 <- stan_glm(data = x,
                  ideology ~ age + race + gender + faminc + gender*faminc,
                  refresh = 0,
                  seed = 220)

print(fit_3, digits = 3)
```

## Temperance
```{r}
age <- 50
race <- "White"
gender <- c("Male", "Female") 
faminc <- c(1,6,12)

newobs <- expand_grid(age, race, gender, faminc)

```

```{r}
x <- add_fitted_draws(newobs, fit_3) %>%
  mutate(faminc = factor(faminc, levels = c(1,6,12)))

x
```
```{r}
library(ggdist)
x %>%
  ggplot(aes(x = .value, y = faminc, fill = gender)) + 
  stat_slab(alpha = 0.5) + 
  labs(title = "Ideology versus Income and Gender",
       subtitle = "Women's ideology varies much more across family incomes",
       x = "Expected Ideology",
       y = "Family Income Category",
       caption = "Source: CCES")
```

